Placeholder

### 2021-02-17 Paper_Histograms.Rmd
Made non-binary/self-defined gender a plot caption for age, gender, employ and ethnicity merged retro graph

#Two columns approach

#ggarrange(arranged_retro_ethnicity_non_white,
#          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
#          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
#          nrow = 3,
#          common.legend =  TRUE)

@@

#Three columns approach
#ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
#          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
#          common.legend = TRUE,
#          ncol = 3,
#          nrow = 2)

@@

```{r Plot retro diagnosis and ethnicity together}

#Note: Adding the data labels for ethnicity or diagnosis looks messy

arranged_retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())# +
#  geom_text(aes(label = n),
#            size = 3,
#            position = position_dodge(width=0.9), 
#            vjust=-0.25)

#Graph 2
arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
theme(axis.text.x = element_text(angle = 70, 
                                 vjust = 0.5,
                                 size = 8)) +
  theme(legend.position = "none") + 
  #theme(legend.title = element_blank()) +
  #geom_text(aes(label = n),
  #          size = 3,
  #          position = position_dodge(width=0.9), 
  #          vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))

arranged_retro_ethnicity_plot <- plot_grid(arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white, labels = "")

ggarrange(retro_diagnosis_plot, arranged_retro_ethnicity_plot,
          common.legend = TRUE)

@@

>>>>

@@

@@

```{r Gender age ethnicity employ retro graph with plot caption}

#Remake gender plot without caption

arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())  +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

```{r plot age gender ethnicity and employ with plot caption}

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))
